---
title: "Jimenez Palmer Coral Paper Analysis Version 2.0"
author: "Xav Harrison"
date: "05/07/2022"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# SECTION 1 SETUP  

## 1.1 Libraries
```{r}
  #### LIBRARIES
        library(tidyverse)
        library(lme4)
        library(brms)
        library(MuMIn)

        options(mc.cores = parallel::detectCores())
    
##### GLOBAL PLOT OPTIONS
             plotopts<-theme(axis.text=element_text(size=18),axis.title=element_text(size=20),strip.text = element_text(size=20),plot.margin = margin(b=1, r=1, t=2, l=1, "lines"),legend.text=element_text(size=15),legend.title=element_text(size=15)) 
           
```

## 1.2 Data Files

```{r}
      #### Temperature Data
        tempdat<-read.csv('sst.csv',header=T)
        
      ### ALL CORAL DATA (6 sites)
        allcoral<-read.csv('Total percent coral cover_all.csv',header=T)  
        
      ### Coral Species Data
        coralspec<-read.csv('spprop_all.csv',header=T)
        
        
      ### Monthly Coral SST 
        monsst_81_20<-read.csv('monSST_Papagayo_1981_2020.csv',header=T)


```

## 1.3 Data Housekeeping 

```{r}

     ### Filter Missign Data Rows
        colnames(allcoral)[1]<-"yr"
        allcoral<- allcoral %>% filter(!is.na(yr))
          head(allcoral)
          
      ## Filter Golb 
        allcoral <- allcoral %>% filter(site!="golb")
        allcoral$site<-factor(allcoral$site)
        
      ## Fix Site IDs
        table(allcoral$site)
        allcoral$site[which(allcoral$site=="pelada")]<-"pel"
        allcoral$site<-factor(allcoral$site)
        
      ##Code to Fix Depths Here
        table(allcoral$depth)
          allcoral$depth<-as.character(allcoral$depth)
          allcoral$depth[which(allcoral$depth=="11.6-9.2")]<-10  
          allcoral$depth[which(allcoral$depth=="5-4.7")]<-5  
          allcoral$depth[which(allcoral$depth=="7-5.5")]<-7  
          allcoral$depth[which(allcoral$depth=="10.9-7.1")]<-11  
          allcoral$depth[which(allcoral$depth=="8.5-10")]<-10  
        table(allcoral$depth)
        
      ## Standardise Time
        allcoral$z_yr<-as.numeric(scale(allcoral$yr))
        table(allcoral$yr)
        
      #Logit Transform Coral Cover For Models 
        allcoral<- allcoral %>% mutate(cover_prop=coralcov/100)
        
        allcoral$cover_prop[which(allcoral$cover_prop==1)]<-0.9999
        allcoral$cover_prop[which(allcoral$cover_prop==0)]<-0.0001
        
        allcoral <- allcoral %>%  mutate(cover_logit= log((cover_prop) / (1-(cover_prop))))
        
        #Additional Housekeeping    
          allcoral$depth<-as.factor(allcoral$depth)
          allcoral$transect<-as.factor(allcoral$transect)
          
  ####### CORAL SPECIES PROPORTIONS     
      
          #Remove NAs
            coralspec<- coralspec[-which(is.na(coralspec$yr)),]
            head(coralspec)
            
            
  ######### TempDat Add Lag Year
          tempdat$yr_lag1<-tempdat$yr+1
     
          

```

## 1.4. Raw Data Summary 

```{r}

     ################### RAW DATA SUMMARY        
        coral_summary<- allcoral %>% group_by(site) %>% summarise(ntransect=length(unique(transect)),nyears=length(unique(yr)),nobs=n(),ndepth=length(unique(depth))) 
coral_summary
 
```

## 1.5 Calculating Mean Coral Per Year and SST / Lagged SST

```{r}
     #Mean Coral Per Measured Year
        allcoralmeans<- allcoral %>% group_by(yr,site) %>% summarise(meancoral=mean(cover_logit))
        nrow(allcoralmeans)
        with(allcoralmeans,table(yr,site))
        
      #Tack on Temperature Data
        allcoralmeans$sst_min<-tempdat$min[match(allcoralmeans$yr,tempdat$yr)]
        allcoralmeans$sst_max<-tempdat$max[match(allcoralmeans$yr,tempdat$yr)]
        allcoralmeans$sst_min_lag1<-tempdat$min[match(allcoralmeans$yr,tempdat$yr_lag1)]
        allcoralmeans$sst_max_lag1<-tempdat$max[match(allcoralmeans$yr,tempdat$yr_lag1)]
 

```

# SECTION 2 MODELLING 

## 2.1 Multivariate Response Models 

### 2.1.1 SST MIN
```{r}

######  CURRENT YEAR MODELS

    ## SST MIN 
             sstmin_mod_all_site<- brm(
              mvbind(sst_min, meancoral) ~ yr +site,
              data = allcoralmeans )
    
                summary(sstmin_mod_all_site)
                bayes_R2(sstmin_mod_all_site)
```


### 2.1.2 SST MAX
```{r}
    ## SST MAX 
             sstmax_mod_all_site<- brm(
              mvbind(sst_max, meancoral) ~ yr +site,
              data = allcoralmeans )
    
                summary(sstmax_mod_all_site)
                bayes_R2(sstmax_mod_all_site) 
            
```

### 2.1.3 LAG+1 SST MIN
```{r}
############ LAG MODELS 
        
    # SST MIN Lag Model
        coc_sstmin_lag<- brm(mvbind(sst_min_lag1, meancoral) ~ yr + site,
                             data = allcoralmeans )
        summary(coc_sstmin_lag)  
                bayes_R2(coc_sstmin_lag)
```

### 2.1.4 LAG+1 SST MAX
```{r}
    #SST Max Lag Model     
        coc_sstmax_lag<- brm(mvbind(sst_max_lag1, meancoral) ~ yr + site,
                             data = allcoralmeans )
        summary(coc_sstmax_lag)   
        bayes_R2(coc_sstmax_lag)

```

## 2.2 Bivariate Model Plotting 

### 2.2.1 SST Min Residual Plot
```{r}

       ########## Plotting 
        library(RColorBrewer)
        library(cowplot)

      #Strip 2019 from AllCoral Data
        allcoralmeans_pre0219<-filter(allcoralmeans,yr<2019)
        
      #Site Dataframe 
        sitedat<-data.frame(siteshort=unique(allcoralmeans$site))
        sitedat$sitelong<-c("San Pedrito","Cocineras","Golondrina","Lara","Dos Emes","Pelada")
        
        sstmin_resid_data<-data.frame(sst_resid=resid(sstmin_mod_all_site)[,,1][,1],coral_resid=resid(sstmin_mod_all_site)[,,2][,1])
        sstmin_resid_data$site<-allcoralmeans_pre0219$site
        sstmin_resid_data$site2<-sitedat$sitelong[match(allcoralmeans_pre0219$site,sitedat$siteshort)]
        sstmin_resid_data$sst_l95<-resid(sstmin_mod_all_site)[,,1][,3]
        sstmin_resid_data$sst_u95<-resid(sstmin_mod_all_site)[,,1][,4]
        sstmin_resid_data$coral_l95<-resid(sstmin_mod_all_site)[,,2][,3]
        sstmin_resid_data$coral_u95<-resid(sstmin_mod_all_site)[,,2][,4]
   
      
      # SST Min Plot With Error Bars 
        sstminplot_eb1<-ggplot(sstmin_resid_data,aes(x=sst_resid,y=coral_resid)) + geom_errorbar(aes(ymin=coral_l95,ymax=coral_u95),width=0.05,color="gray60") + geom_errorbarh(aes(xmin=sst_l95,xmax=sst_u95),height=0.25,color="gray60")
        sstminplot_eb2<- sstminplot_eb1 + geom_smooth(method="lm") + geom_point(aes(fill=site2),size=5,shape=21) 
        sstminplot_eb3<- sstminplot_eb2 + labs(x="Minimum SST Residuals",y="Mean Coral Cover Residuals (Logits)",fill="Site") + theme_bw()+ plotopts + theme(legend.position = "bottom")
        sstminplot_eb4<- sstminplot_eb3 + scale_fill_brewer(palette = "Set2")
        sstminplot_eb4   
        
        #Save Plpots
              ggsave2('SST Min Coral Cover Residual Correlation Error Bars.pdf',sstminplot_eb4,width=9,height=7)
                ggsave2('SST Min Coral Cover Residual Correlation Error Bars.jpeg',sstminplot_eb4,width=9,height=7)


```

### 2.2.2 SST MAX Residual Plot

```{r}

     
      #Extract Residuals      
        sstmax_resid_data<-data.frame(sst_resid=resid(sstmax_mod_all_site)[,,1][,1],coral_resid=resid(sstmax_mod_all_site)[,,2][,1])
        sstmax_resid_data$site<-allcoralmeans_pre0219$site
        sstmax_resid_data$site2<-sitedat$sitelong[match(allcoralmeans_pre0219$site,sitedat$siteshort)]
        sstmax_resid_data$sst_l95<-resid(sstmax_mod_all_site)[,,1][,3]
        sstmax_resid_data$sst_u95<-resid(sstmax_mod_all_site)[,,1][,4]
        sstmax_resid_data$coral_l95<-resid(sstmax_mod_all_site)[,,2][,3]
        sstmax_resid_data$coral_u95<-resid(sstmax_mod_all_site)[,,2][,4]
   
      
      # SST Min Plot With Error Bars 
        sstmaxplot_eb1<-ggplot(sstmax_resid_data,aes(x=sst_resid,y=coral_resid)) + geom_errorbar(aes(ymin=coral_l95,ymax=coral_u95),width=0.05,color="gray60") + geom_errorbarh(aes(xmin=sst_l95,xmax=sst_u95),height=0.25,color="gray60")
        sstmaxplot_eb2<- sstmaxplot_eb1 + geom_smooth(method="lm") + geom_point(aes(fill=site2),size=5,shape=21) 
        sstmaxplot_eb3<- sstmaxplot_eb2 + labs(x="Maximum SST Residuals",y="Mean Coral Cover Residuals (Logits)",fill="Site") + theme_bw()+ plotopts + theme(legend.position = "bottom")
        sstmaxplot_eb4<- sstmaxplot_eb3 + scale_fill_brewer(palette = "Set2")
        sstmaxplot_eb4 
        
    ## Save Plots    
        ggsave2('SST Max Coral Cover Residual Correlation Error Bars.pdf',sstmaxplot_eb4,width=9,height=7)
        ggsave2('SST Max Coral Cover Residual Correlation Error Bars.jpeg',sstmaxplot_eb4,width=9,height=7)



```

# SECTION 3: SITE-LEVEL CORAL DECLINE MODELS 

## 3.1 Models

### 3.1.1 Cocineras 
```{r}

######### COCINERAS 

#Data
  coc<- allcoral %>% filter(site=="coc") %>% mutate(z_yr=as.numeric(scale(yr)))

   
      cf1<-lmer(cover_logit ~ poly(z_yr,2)  + (1|depth) + (1|transect) ,data=coc)
      cf2<-lmer(cover_logit ~ z_yr  + (1|depth) + (1|transect) ,data=coc)
      model.sel(cf1,cf2)
```

### 3.1.2 Dos Emes

```{r}

######### DOS EMES
  mm<- allcoral %>% filter(site=="mm") %>% mutate(z_yr=as.numeric(scale(yr)))

      mf1<-lmer(cover_logit ~ poly(z_yr,2)  + (1|depth) + (1|transect) ,data=mm)
      mf2<-lmer(cover_logit ~ z_yr  + (1|depth) + (1|transect) ,data=mm)
      model.sel(mf1,mf2)
```

### 3.1.3 Lara
```{r}

######## LARA 
  lara<- allcoral %>% filter(site=="lara") %>% mutate(z_yr=as.numeric(scale(yr)))

      lf1<-lmer(cover_logit ~ poly(z_yr,2)  + (1|depth) + (1|transect) ,data=lara)
      lf2<-lmer(cover_logit ~ z_yr  + (1|depth) + (1|transect) ,data=lara)
      model.sel(lf1,lf2)
    
```

### 3.1.4 Golondrina
```{r}
########## GOLONDRINA   
      gol<- allcoral %>% filter(site=="gol") %>% mutate(z_yr=as.numeric(scale(yr)))

      gf1<-lmer(cover_logit ~ poly(z_yr,2)  + (1|depth) + (1|transect) ,data=gol)
      gf2<-lmer(cover_logit ~ z_yr  + (1|depth) + (1|transect) ,data=gol)
      model.sel(gf1,gf2)
```

### 3.1.5 San Pedrito

```{r}

########## SAN PEDRITO   
      sp<- allcoral %>% filter(site=="sp") %>% mutate(z_yr=as.numeric(scale(yr)))

      sf1<-lmer(cover_logit ~ poly(z_yr,2)  + (1|depth) + (1|transect) ,data=sp)
      sf2<-lmer(cover_logit ~ z_yr  + (1|depth) + (1|transect) ,data=sp)

      model.sel(sf1,sf2)
      
```

### 3.1.6 Pel 
```{r}
########## PEL
     pel<- allcoral %>% filter(site=="pel") %>% mutate(z_yr=as.numeric(scale(yr)))

      pf1<-lmer(cover_logit ~ poly(z_yr,2)  + (1|depth) + (1|transect) ,data=pel)
      pf2<-lmer(cover_logit ~ z_yr  + (1|depth) + (1|transect) ,data=pel)
      model.sel(pf1,pf2)
       
        
```

## 3.2 Predictions  

### 3.2.1 Bayesian Version of Each Model 

```{r}

     coc_pred<- brm(cover_logit ~ poly(z_yr,2) + (1|depth) + (1|transect),data=coc,control=list(adapt_delta=0.99),iter=10000,warmup=2000,thin=10)
     sp_pred<- brm(cover_logit ~ poly(z_yr,2) + (1|depth) + (1|transect),data=sp,control=list(adapt_delta=0.99),iter=10000,warmup=2000,thin=10)
     mm_pred<- brm(cover_logit ~ poly(z_yr,2) + (1|depth) + (1|transect),data=mm,control=list(adapt_delta=0.99),iter=10000,warmup=2000,thin=10)
     lara_pred<- brm(cover_logit ~ poly(z_yr,2) + (1|depth) + (1|transect),data=lara,control=list(adapt_delta=0.99,max_treedepth=15),iter=10000,warmup=2000,thin=10)
     gol_pred<- brm(cover_logit ~ poly(z_yr,2) + (1|depth) + (1|transect),data=gol,control=list(adapt_delta=0.99),iter=10000,warmup=2000,thin=10)
     pel_pred<- brm(cover_logit ~ poly(z_yr,2) + (1|depth) + (1|transect),data=pel,control=list(adapt_delta=0.99),iter=10000,warmup=2000,thin=10)


```

### 3.2.2 Prediction Output
```{r}

################## PREDICTIONS    
      
      ## Prediction Models
        #  coc_r1; sp_mod1; gol_mod_linear; lara_mod_linear
      
    #Back Transform Data
      coral_vals<- allcoral %>% group_by(site) %>% summarise(meanyr=mean(yr),sdyr=sd(yr))
      
     coc_cond<-conditional_effects(coc_pred) 
     coc_cond<-coc_cond[[1]]
     coc_cond<- coc_cond %>% mutate(coral_mean=plogis(estimate__),u95=plogis(upper__),l95=plogis(lower__),yr=(z_yr*as.numeric(coral_vals[1,3]) + as.numeric(coral_vals[1,2])),site="Cocineras")
     
     sp_cond<-conditional_effects(sp_pred) 
     sp_cond<-sp_cond[[1]]
     sp_cond<- sp_cond %>% mutate(coral_mean=plogis(estimate__),u95=plogis(upper__),l95=plogis(lower__),yr=(z_yr*as.numeric(coral_vals[6,3]) + as.numeric(coral_vals[6,2])),site="San Pedrito")
    
     gol_cond<-conditional_effects(gol_pred) 
     gol_cond<-gol_cond[[1]]
     gol_cond<- gol_cond %>% mutate(coral_mean=plogis(estimate__),u95=plogis(upper__),l95=plogis(lower__),yr=(z_yr*as.numeric(coral_vals[2,3]) + as.numeric(coral_vals[2,2])),site="Golondrina")
    
     lara_cond<-conditional_effects(lara_pred) 
     lara_cond<-lara_cond[[1]]
     lara_cond<- lara_cond %>% mutate(coral_mean=plogis(estimate__),u95=plogis(upper__),l95=plogis(lower__),yr=(z_yr*as.numeric(coral_vals[3,3]) + as.numeric(coral_vals[3,2])),site="Lara")
     
     mm_cond<-conditional_effects(mm_pred) 
     mm_cond<-mm_cond[[1]]
     mm_cond<- mm_cond %>% mutate(coral_mean=plogis(estimate__),u95=plogis(upper__),l95=plogis(lower__),yr=(z_yr*as.numeric(coral_vals[4,3]) + as.numeric(coral_vals[4,2])),site="Dos Emes")
     
    pel_cond<-conditional_effects(pel_pred) 
     pel_cond<-pel_cond[[1]]
     pel_cond<- pel_cond %>% mutate(coral_mean=plogis(estimate__),u95=plogis(upper__),l95=plogis(lower__),yr=(z_yr*as.numeric(coral_vals[5,3]) + as.numeric(coral_vals[5,2])),site="Pelada")
```

### 3.2.3 Facet Plot of All Corals
```{r}
    #Combine
     coral_predict_combo<-rbind(sp_cond,coc_cond,gol_cond,lara_cond,mm_cond,pel_cond)
   
    #Fite Site ID in Full Data
     coral_predict_combo$site_long<-coral_predict_combo$site
     coral_site_translate<-data.frame(short=c("coc","sp","gol","lara","mm","pel"),long=c("Cocineras","San Pedrito","Golondrina","Lara","Dos Emes","Pelada"))
     allcoral$site_long<-coral_site_translate$long[match(allcoral$site,coral_site_translate$short)]
     
    #Factor for Correct Plotting Order
     coral_predict_combo$site_long<-factor(coral_predict_combo$site_long,levels=c("San Pedrito","Cocineras","Golondrina","Lara","Dos Emes","Pelada"))
     
    ## Labeller for Facets 
     dat_text <- data.frame(
  label = c("A", "B", "C","D","E","F"),
  site_long=c("San Pedrito","Cocineras","Golondrina","Lara","Dos Emes","Pelada")
        )
     
    #Relabel Facets in Dataframe
     newsitelabeldf<-data.frame(old=c("San Pedrito","Cocineras","Golondrina","Lara","Dos Emes","Pelada"),new=c("A. San Pedrito","B. Cocineras","C. Golondrina","D. Lara","E. Dos Emes","F. Pelada"))
coral_predict_combo$newfacet<- newsitelabeldf[,2][match(coral_predict_combo$site_long,newsitelabeldf[,1])]
allcoral$newfacet<-newsitelabeldf[,2][match(allcoral$site_long,newsitelabeldf[,1])]

  ########### PLOT OF RAW DATA AND PREDICTED VALUES   
     plotopts<-theme(axis.text=element_text(size=18),axis.title=element_text(size=20),strip.text = element_text(size=25),plot.margin = margin(b=1, r=1, t=2, l=1, "lines"),legend.text=element_text(size=15),legend.title=element_text(size=15)) 
     
     coralplot1<-ggplot() 
     coralplot2<- coralplot1 + geom_ribbon(data=coral_predict_combo,aes(x=yr,ymin=l95,ymax=u95),fill="lightgrey",alpha=0.5) + geom_line(data=coral_predict_combo,aes(x=yr,y=coral_mean)) + facet_wrap(.~newfacet) + scale_x_continuous(n.breaks=15)
     coralplot3<- coralplot2 + theme_bw() + plotopts +  geom_point(data=allcoral,aes(x=yr,y=cover_prop,fill=newfacet),shape=21,size=5) + scale_fill_brewer(palette="Set2") +guides(fill=F) + labs(y="Proportion Coral Cover",x="Year") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
     coralplot4<-coralplot3 #+ geom_text(data    = dat_text, mapping = aes(x = -Inf, y = -Inf, label = label),hjust   = -0.5, vjust   = -0.5,size=15)
     coralplot4
     
   ## Save Plots  
     library(cowplot)
     ggsave2('Coral Raw Data and Predictions.pdf',coralplot4,width=18,height=12)
     ggsave2('Coral Raw Data and Predictions.jpeg',coralplot4,width=18,height=12)
    
```




# SECTION 4: CORAL COMMUNITY TURNOVER

## 4.1 Data Cleaning 
```{r}

  ### Fix Site IDs (deprecated - now filtering out Golb subsite)
        coralspec$oldsite<-coralspec$site
        # coralspec$site[which(coralspec$site=="golb")]<-"gol"
        coralspec$site[which(coralspec$site=="Lara")]<-"lara"

  ## Filter Out Golb 
        coralspec <- coralspec %>% filter(site !="golb")
        table(coralspec$site)

      ##Code to Fix Depths Here
        table(coralspec$depth)
          coralspec$depth<-as.character(coralspec$depth)
          coralspec$depth[which(coralspec$depth=="11.6-9.2")]<-10  
          coralspec$depth[which(coralspec$depth=="5-4.7")]<-5  
          coralspec$depth[which(coralspec$depth=="7-5.5")]<-7  
          coralspec$depth[which(coralspec$depth=="10.9-7.1")]<-11  
          coralspec$depth[which(coralspec$depth=="8.5-10")]<-10  
        table(coralspec$depth)
        
        
    ## Every Row Should Sum to 1 
        colnames(coralspec)
        coralspec$propsum<-apply(coralspec[,5:10],1,sum)
        
        #write.csv(coralspec,'Coral Species Prop with Sum Proportions.csv')
        
```

## 4.2 Group Means in Two Stages 
```{r}

#Summarise Coral Community Cover By Transect/Site/Year Combo Then By Year / Site
  coralsum1<- coralspec %>% group_by(site,transect,yr) %>% summarise(poc=mean(poc),pav=mean(pav),por=mean(por),ps=mean(ps),gar=mean(gar),tub=mean(tub)) %>% group_by(site,yr) %>% summarise(poc=mean(poc),pav=mean(pav),por=mean(por),ps=mean(ps),gar=mean(gar),tub=mean(tub)) #%>% transmute(yr=as.factor(yr))
  head(coralsum1)
  coralsum1$yr<-as.factor(coralsum1$yr)
  
#Pivot Longer
  coralsum_long<- coralsum1 %>% pivot_longer(cols=poc:tub,names_to = "coralspecies",values_to="proportion")
  head(coralsum_long)
  
#Check Sums Oer Site/Year 
  coralsum_long %>% group_by(site,yr) %>% summarise(sum=sum(proportion))

```

##4.3 Stacked Bar Plot 
```{r}

#Long Site Names 
  coralsum_long$site_long<-sitedat[,2][match(coralsum_long$site,sitedat[,1])]

#Proper Coral Names 
  coraldat<-data.frame(coralshort=unique(coralsum_long$coralspecies),corallong=c("Pocillopora","Pavona","Porites","Psammocora","Gardineroseris","Tubastrea"))
    coralsum_long$coral_long<-coraldat[,2][match(coralsum_long$coralspecies,coraldat[,1])]
    
 #Factor for Correct Plotting Order
     coralsum_long$site_long<-factor(coralsum_long$site_long,levels=c("San Pedrito","Cocineras","Golondrina","Lara","Dos Emes","Pelada"))
     
  #Numeric Year for Proper Plotting of X Axis   
    coralsum_long$yr=as.numeric(as.character(coralsum_long$yr))

#Stacked Bar
  coralstack1<- ggplot(coralsum_long,aes(x=yr,y=proportion,fill=coral_long)) + geom_bar(position = "fill",stat="identity")
  coralstack2<- coralstack1 + scale_fill_brewer(palette="Dark2") + facet_wrap(.~site_long) +  scale_x_continuous(n.breaks=15)
  coralstack3<- coralstack2 + theme_bw() + plotopts + labs(fill="Genus",y="Proportion Coral Genus",x="Year") + theme(axis.text.x = element_text(angle=45,vjust = 1, hjust=1),legend.position="bottom",legend.text = element_text(size=20),legend.title=element_text(size=20)) + guides(fill=guide_legend(nrow=2,byrow=TRUE))
  coralstack3
  
  ## Save Plots
     library(cowplot)
     ggsave2('Coral Cover Proportions.pdf',coralstack3,width=14,height=10)
     ggsave2('Coral Cover Proportions.jpeg',coralstack3,width=14,height=10)
 ```


## 4.4 Quick ~Check of Two 'Gol/Golb' Sites

```{r}

#Summarise Coral Community Cover By Transect/Site/Year Combo Then By Year / Site
  golbsum1<- coralspec %>% filter(oldsite %in% c("golb","gol"))# %>% group_by(site,transect,yr) %>% summarise(poc=mean(poc),pav=mean(pav),por=mean(por),ps=mean(ps),gar=mean(gar),tub=mean(tub)) %>% group_by(site,yr) %>% summarise(poc=mean(poc),pav=mean(pav),por=mean(por),ps=mean(ps),gar=mean(gar),tub=mean(tub)) #%>% transmute(yr=as.factor(yr))
  head(golbsum1)
  table(golbsum1$oldsite)

#Pivot Longer
  golbsum_long<- golbsum1 %>% pivot_longer(cols=poc:tub,names_to = "coralspecies",values_to="proportion")
  head(golbsum_long)
  golbsum_long$yr<-factor(golbsum_long$yr)
  table(golbsum_long$oldsite)
  
#Stacked Bar
  golbstack1<- ggplot(golbsum_long,aes(x=yr,y=proportion,fill=coralspecies)) + geom_bar(position = "fill",stat="identity")
  golbstack2<- golbstack1 + scale_fill_brewer(palette="Set1") + facet_wrap(.~oldsite) #+  scale_x_continuous(n.breaks=15)
  golbstack3<- golbstack2 + theme_bw() + plotopts + labs(fill="",y="Proportion Coral Genus",x="Year") + theme(axis.text.x = element_text(angle=45,vjust = 1, hjust=1),legend.position="bottom",legend.text = element_text(size=20),legend.title=element_text(size=20)) + guides(fill=guide_legend(nrow=2,byrow=TRUE))
  golbstack3
  
#Check Sums Oer Site/Year 
  #coralsum_long %>% group_by(site,yr) %>% summarise(sum=sum(proportion))

```

# SECTION 5: PROPORTION OF MONTHS 

```{r}

## Set Thresholds 
upper_threshold<-29.7
lower_threshold<-25.7

############## PLOT OF PROPORTION MONTHS ABOVE OR BELOW THRESHOLDS

            head(monsst_81_20)
            
          #Strip Out Year 
            monsst_81_20$yr<-(unlist(lapply(strsplit(as.character(monsst_81_20$monthyear),"-"),"[",2)))
            
          #Clumsy padding of years around the Year 2000 
            monsst_81_20$yrlong<-ifelse(monsst_81_20$yr>80,paste0("19",monsst_81_20$yr),paste0("20",monsst_81_20$yr))
            
          #Summarise
            tempsum<- monsst_81_20 %>% group_by(yrlong) %>% summarise(above_upper=mean(SST>upper_threshold),below_lower=mean(SST<lower_threshold)) %>% ungroup() #%>% filter(yrlong<20)
            
          #Flip to Long Format 
            tempsum_long<-tempsum %>% pivot_longer(cols=c("above_upper","below_lower"),names_to="trend")
            
          #Custom Facet Labels   
            #trendlabs <- 
            trendlabs1<-expression(paste("Proportion Months Above 29.7",~degree,"C"))
            trendlabs2<-expression(paste("Proportion Months Below 25.7",~degree,"C"))
            trendlabs<-c(trendlabs1,trendlabs2)
names(trendlabs) <- c("above_upper","below_lower")

          #Suppress Plotting of Zeroes
            tempsum_long$value_suppress0<-tempsum_long$value
            tempsum_long$value_suppress0[which(tempsum_long$value==0)]<-NA

          #FACET Plot
            # tempplot1<-ggplot(tempsum_long,aes(x=yrlong,y=value_suppress0,group=trend))+ geom_point(shape=21,size=5,aes(fill=trend))  + theme_classic()
            # tempplot2<- tempplot1 + facet_grid(trend~.,label='label_parsed') + labs(x="Year",y="Proportion Months Breaching Threshold Temperature")
            # tempplot3<-  tempplot2 + plotopts + theme(axis.text.x = element_text(angle=45,hjust=1)) + guides(colour=FALSE)
            # tempplot3
            # ggsave2('Average Prop Months Above Temp.pdf',tempplot3,width=15,height=8)
            
            
      ### Alternative way of Plotting 
            #expression(paste("Proportion Months",~degree,"C"))
            
          tempsum_long$trend<-factor(tempsum_long$trend)
          library(scales)
          abovelab<- expression("Proportion Months Above 29.7",~degree,"C")
          belowlab<-expression("Proportion Months Below 25.7",~degree,"C")
          
  #         tempsum_long = tempsum_long %>% 
  # mutate(trend_code = recode_factor(trend, "above_upper" = abovelab, "below_lower" = belowlab))  
  #           
            # tempplot1<-ggplot(tempsum_long,aes(x=yrlong,y=value,group=trend))+ geom_line(aes(colour=trend)) + geom_point(size=5,shape=21,fill="white") + theme_bw() 
            # tempplot2<- tempplot1 + labs(x="Year",y="Proportion of Months",col=expression(paste("Temperature Breach",~degree,"C")))
            # tempplot3<-  tempplot2 + plotopts + theme(axis.text.x = element_text(angle=45,hjust=1),legend.position="top") + scale_colour_manual(labels=c("Below 25.7","Above 29.7"),breaks=c("below_lower","above_upper"),values=c("blue","red"))
            # tempplot3
            # 
            # #ggsave2('Temperature Threshold Graph v2.pdf',tempplot3,width=12,height=8)
            # 
            
            
        ###### Version 2 of Above Following Peer Review July 2022
            tempplot_new1<-ggplot(tempsum_long,aes(x=as.numeric(yrlong),y=value_suppress0,group=trend)) + geom_point(size=8,shape=21,aes(fill=trend)) + theme_bw() 
            tempplot_new2<- tempplot_new1 + labs(x="Year",y="Proportion of Months",fill=expression(paste("Temperature Breach",~degree,"C")))
            tempplot_new3<-  tempplot_new2 + plotopts + theme(axis.text.x = element_text(angle=45,hjust=1),legend.position="top") + scale_fill_manual(labels=c("Below 25.7","Above 29.7"),breaks=c("below_lower","above_upper"),values=c("dodgerblue","indianred1"))
            tempplot_new4<- tempplot_new3 + scale_x_continuous(breaks=seq(1981,2019,2))
            tempplot_new4
            ggsave2('Temperature Threshold Graph v3 Jul22 PostReview.pdf',tempplot_new4,width=10,height=7)

```
